---
title: 'Suppelemental Figure 3: Impact of multiple-imaged plankton'
---

To assess the impact of duplicate images, for all casts in AE1912, the most abundant plankton taxonomic groups (Rhizaria, *Trichodesmium*, Copepods, *Eumalacostraca*) were all identified as either an independent observation or a "technically not duplicate" - a multiple instance of the same individual recorded in multiple pictures.

The abundance of these taxa were then calculated with two possible methods:
1- All technically not duplicate images were counted as independed observations. Density was then calculated using the volume sampled as determined by the UVP
2- Technically not duplicate images were removed. When 

Method 1 is displayed by black points while Method 2 is displayed by blue points.

```{r set up, warning = F, echo=FALSE}
rm(list = ls())
library(ggplot2)
library(ggalt)
dup_plots <- readRDS('../Output/supp_fig_03_dup-plots.rds')
```

```{r plots, warning = F, fig.cap='Sup Fig 3. Imact of multiple-imaged organisms on density estimates for specific taxa on individual casts in 20m bins. Black points show inclusion of multiples, blue points show exclusion.'}
print(dup_plots)
```