---
title: "Supplemental Figure 4: All Density Profiles"
---
  
Density profiles of comparable taxa are shown when measured by the MOCNESS/ZOOSCAN and the UVP. UVP estimates were calculated two ways. In one method, similar UVP casts are pooled then the density of organisms in a depth bin were calculated $$\frac{\sum_{i}^{N}individuals_{i}}{\sum_{i}^{N}volume sampled_{i}}$$. The other method, density is calculated in individual uvp casts, then averaged between all similar casts: $$\frac{\sum_{i=1}^{N} \frac{individuals_{i}}{volume sampled_{i}}}{N}$$ For all i casts, with a total of N casts.

```{r}
rm(list = ls())
library(cowplot)
library(ggplot2)
plot_list <- readRDS('../Output/main_fig_03_profile-density-comparison.rds')
```


```{r All-Plots, fig.cap='Supplemental Figure 4. Density profiles of all taxa. Pooled-UVP cast estimates are shown as barplots. Averaged-UVP casts estimates are shown by points with standard deviation shown.'}
#| column: body-outset
plot_grid(for(i in 1:length(plot_list)){print(plot_list[[i]] + theme(legend.position = 'bottom'))}, ncol = 3)
```