---
title: Supplemental Figure 3 - Full size range of MOCNESS
---

As noted in the core paper, the MOCNESS samples a much larger range of sized-plankton than the UVP. For comparison, we look at MOCNESS-collected plankton which are equal to or larger than the smallest observed UVP plankton (0.894mm). The comparison of that size range can be found [here](./main_analysis_01.html). In this analysis, the full size range of the MOCNESS is shown. Additionally, the table below shows the proportion of MOCNESS-collected plankton which are excluded because they are smaller than 0.894mm

------------------------------------------------------------------------

```{r set-up, warning=F}
rm(list = ls())
library(ggplot2)
library(DT)

plot_list <- readRDS('../Output/supp_fig_01_full-size-distribution.rds')
dat_list <- readRDS('../Output/data_01_size-range-dfs.rds')
```

```{r Plotting, fig.height=10, out.width='100%',fig.cap= 'Size distributions for select taxa.', dpi= 300}
#| column: body-outset
print(plot_list)
```

```{r Table}
#| column: screen-inset
comp_taxo <- c('Chaetognatha', 'Annelida', 'Copepoda', 'Shrimp-like',
               'Ostra/Clado')

moc_dat <- dat_list$moc_full
moc_dat <- moc_dat[moc_dat$taxo_name %in% comp_taxo,]

get_percentile <- function(taxo) {
  value <- ecdf(moc_dat$calc_esd[moc_dat$taxo_name == taxo])(0.894)
  return(round(value*100, 2))
}

moc_tab <- data.frame(
  taxa = sort(unique(moc_dat$taxo_name)),
  `% Moc Excluded` = sapply(sort(unique(moc_dat$taxo_name)),
                            get_percentile)
)

datatable(moc_tab, class = 'hover', colnames = c('Taxa', '% Moc Excluded'),
          rownames = FALSE, caption = 'Mocness-collected taxa and percent excluded by 0.894 size cut off')
```